\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{iccv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bbm}
% Include other packages here, before hyperref.

\usepackage{color}
\usepackage{enumerate}


\newcommand{\cxj}[1]{\textcolor[rgb]{1.00,0.00,0.00}{(cxj: #1)}}
\newcommand{\mdf}[1]{\textcolor[rgb]{0.00,0.00,1.00}{#1}}
\newcommand{\bobo}[1]{\textcolor[rgb]{0.00,0.30,0.00}{(mbobo: #1)}}
\newcommand{\vb}[1]{\mathbf{#1}}
\newcommand{\comments}[1]{}


% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \iccvfinalcopy % *** Uncomment this line for the final submission

\def\iccvPaperID{****} % *** Enter the ICCV Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ificcvfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE
\title{ShapeCNN: Shape-Constrained Neural Network \bobo{change a name? maybe the main ideal is not constraint} for Membrane Structure Segmentation via Joint Pooling Operation}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\d
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}



\maketitle
%\thispagestyle{empty}


%%%%%%%%% ABSTRACT
\begin{abstract}
   Accurate segmentation of biomembrane objects is a crucial step to obtain morphological statistics in biomedical analysis.
   However in many scenarios, prior shape knowledge about biomedical objects is available, which is especially useful for segmenting dense and regular objects.
   In this paper, we introduce a new approach, named shape-constrained neural network (SCNN), by incorporating prior shape knowledge about plausible components into neural network.
   Our SCNN is a multi-task learning framework that simultaneously predicts objectness scores and parameterized expression of object shape at each position as auxiliary.
   The auxiliary information are utilized to separate the segmented objects into individuals, and further optimize the objects shape.
   Moreover, a novel joint pooling operation is developed as a trainable layer to optimize both predicted objectness scores and shape parameters, which are subsequently fused into final segmentation masks.
   The whole process is efficient and optimized end-to-end.
   Experiments on synaptic vesicle segmentation and glands segmentation demonstrate the effectiveness of our approach.
   And we expect our method to empower more works to incorporate more complicate shape constraints into segmentation tasks through deep convolutional neural networks.
   Code is made publicly available at \url{https://github.com/mboboUSTC/SCNN.git}.

\end{abstract}

%%%%%%%%% BODY TEXT
\input{introduction}
\input{algorithm}
\input{results}

\section{Conclusion}








{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}
